\begin{abstract}

%Fitness applications have become increasingly popular to record workouts, an indicator of how important it is to exercise and keep fit. Research was conducted to find out the ways in which these applications try to engage the user to encourage them to exercise more, such as adding an element of gamification in an attempt to motivate the user.

In today's society, it is extremely important to keep fit and exercise. This can be seen by the increasing popularity of fitness applications over the recent years. The problem that is posed by fitness apps is to try to engage with the user in an attempt to motivate them to exercise more. Various methods were researched to try and solve this problem, in particular exercising in groups and using gamification, both of which were employed in this project.

This project aims to provide a means to encourage people to exercise more and discover more about the world around them. We have created an iOS application that allows the user to track the walks they go on and view points of interest around them -- specifically historical plaques that commemorate notable people. We have also created a back-end API that the mobile app can interact with to store and retrieve user data. The application can be used anywhere in the world, although rural areas may contain a far fewer number of points of interest, which may hinder your experience.

We then tested and evaluated the application with real users to assess whether it had an impact on how often they exercise and whether they were able to discover new places in their area. The results obtained suggest that the application produced did have a positive impact on the user in the areas described above, but with a few limitations that could be improved on in the future.

\end{abstract}