\chapter{Design}

\section{Overview}

The project can be split into two main sections -- the front-end mobile application and the back-end server to store data and communicate with the mobile app.

These two sections link together very closely and are both required to produce a working implementation. It is therefore extremely important to not only consider the design of the user interface but also more technical aspects, such as the way the user's data is stored in the database and how the API will communicate with the mobile app.

\section{Technology Choices}

The first part of the design of the project is to consider which technologies to use. The technologies that I chose stemmed either from the background research I conducted in the previous section or previous personal knowledge.

%\subsection{Mobile Operating System}

% move section in background to here?

\subsection{Version Control}

\subsection{Third-party APIs}

As discussed in Section \ref{subsection:background-apis}, Apple Maps very well integrated with the Core Location framework in iOS, which makes it easy to deal with displaying the user's location on a map. It also provides convenient functions for coordinate conversions and calculating distances between two coordinates, which is useful for this project when trying to calculate the distance of a tracked walk.

For these reasons, I chose to use Apple Maps and their MapKit framework as the source of maps within the application. The one issue that I previously discussed with using this framework over Google Maps was the lack of detail in some areas of the maps. This factor was not deemed important enough to impact my decision and did not outweigh the benefits of the MapKit framework, as listed above.

% points of interest APIs

\subsection{Server Architecture}

Before deciding what technologies to use for the server, such as which programming language to use, we must consider the type of architectural style to use. The aim of the API exposed by the server is to provide an abstraction between complex database queries and provide functionality that a client can use to query and update details. The Representational state transfer (REST) architectural principle fit the needs for this aim very well. Every component in a RESTful web service is a resource that can be accessed via the standard HTTP methods such as \textit{GET}, \textit{POST} and \textit{DELETE}. In comparison with other web services, such as the Simple Object Access Protocol (SOAP), RESTful services have much less overhead when sending data due to the extra XML header information sent when using SOAP.

With the architecture chosen, I assessed the options for the language to write the API in. There are a wide range of programming languages that could be used, and it came down to personal preference and how well it would suit the needs for this project. The popular options include PHP, Ruby, Python and Node.js ***ref*** -- the server-side environment run in Javascript. The only language in this list that I have experience in is Python, which would mean I would have to spend less time learning the language if I were to choose it. However, the advantage of Node.js for the purpose of this project is that objects in Javascript are built using Javascript Object Notation (JSON). RESTful web services support the use of multiple different data formats to serialise responses from the server, including HTML, XML and JSON. By choosing Node.js as the server language and JSON as the data type, I was able to easily parse data from HTTP requests and send responses in JSON despite not having any previous experience with Javascript.

\subsection{Database}

There are two types of database that could be used -- relational or non-relational. Relational databases are based upon relational algebra where data is stored in tables with queries to this data in the form of Structured Query Language (SQL). Each table in a relational database normally identifies a type of entity, and each instance of that entity is uniquely identifiable so that it can be referenced in other tables. SQL therefore supports the querying of this data across multiple tables using relational operators such as joining two tables. The most used services to model data in a relational database are MySQL and PostgreSQL, with the latter providing support for storing arrays -- which is useful for this project to store the coordinates of a walk.

The opposite of this data model is a non-relational, or NoSQL, database in which each data entry is stored as a JSON-like document. This approach has many advantages for this project, primarily the similarities in the way that the data is stored to JSON that is used in the API. As a result, data can be queried or inserted directly from a network request without any type conversions. NoSQL databases also have the benefit of faster query speeds and the ability to scale data horizontally, an important factor to consider when designing a database.

The leading service to use for managing document-based NoSQL databases is MongoDB. It was used in this project especially due to its similar use of Javascript and JSON, both of which are already employed in the Node.js API. I also used a popular object data modelling library, Mongoose ***ref***, which helped with validation and allowed me to define schemas for each of the type entities.

\subsection{API Deployment}

I opted to host my API on the platform as a service Heroku ***ref***, with the alternative being Imperial's Cloudstack service run by the Department of Computing. Having had little experience with either of these services, I learned that Heroku had certain features that gained itself an advantage over Cloudstack. Heroku is integrated with Github very well, my chosen version control platform, supporting automatic deployment when commits are made which can also be dependent on the results of continuous integration tests. Heroku also has a number of add-ons that can be used on your web applications, including mLab -- a cloud-hosted version of MongoDB that is essential for me following on from the choice of database discussed in the previous section. Conversely, Cloudstack does not support MongoDB outright and would therefore have taken more effort to set it up.

% heroku vs imperial cloudstack
% heroku has mlab add-on

\subsection{File Storage}

% aws s3

\section{User Interface Design}

% design of app
% how screens are organised
% survey

% mvc
% tab-bar
% human interface guidelines

\section{API Design}

% REST model, specific endpoints, etc.

\subsection{Database Models}

% types of models – user, walk, invite, etc.

\subsection{Endpoint Structure}